### 2020-08-10 data/draft-publications.tex
improvements for next year

\begin{enumerate}
\item A. Banerjee: Spectra as universal objects in categories of supports in {\em Banach Center Publications(Quantum Dynamics Proceedings)} Ludwik Dabrowski, Ryszard Nest, Adam Skalski (ed.) , Banach Center Publications , IMPAN, Warsaw, Poland (2020), (accepted).
\item IMPAN, Warsaw, Poland: 2020 in {\em (accepted)} No (ed.)   ().
\item S. Ghara and G. Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G. Douglas Memorial Volume} Curto, R.E., Helton, W., Lin, H., Tang, X., Yang, R., Yu, G. (ed.) , Operator Theory: Advances and Applications , Birkhauser (2020).
\item Birkhauser: 2020 in {\em } Yes (ed.) , Gadadhar Misra , Decomposition of the tensor product of two Hilbert modules (Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G. Douglas Memorial Volume), R. Curto, W. Helton, H. Lin, X. Tang, R. Yang, G. Yu.
\item Decomposition of the tensor product of two Hilbert modules: Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G. Douglas Memorial Volume in {\em R. Curto, W. Helton, H. Lin, X. Tang, R. Yang, G. Yu} Operator Theory: Advances and Applications (ed.) , Birkhauser , 2020 (), No.
\item 2020:  in {\em No}  (ed.)   ().
\end{enumerate}

>>>>

\begin{enumerate}
\item A. Banerjee: Spectra as universal objects in categories of supports in {\em Banach Center Publications(Quantum Dynamics Proceedings)} Ludwik Dabrowski, Ryszard Nest, Adam Skalski (ed.) , Banach Center Publications , IMPAN, Warsaw, Poland (2020), (accepted).
\item S. Ghara and G. Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G. Douglas Memorial Volume} Curto, R.E., Helton, W., Lin, H., Tang, X., Yang, R., Yu, G. (ed.) , Operator Theory: Advances and Applications , Birkhauser (2020).
\item Gadadhar Misra: Decomposition of the tensor product of two Hilbert modules in {\em Operator Theory, Operator Algebras and Their Interactions with Geometry and Topology Ronald G. Douglas Memorial Volume} R. Curto, W. Helton, H. Lin, X. Tang, R. Yang, G. Yu (ed.) , Operator Theory: Advances and Applications , Birkhauser (2020).
\end{enumerate}
